Data Archiving Attitudes

### 2018-03-20 manuscript.Rmd
make .md

---
title: "Data Archiving Attitudes"
author: "Heather A. Piwowar, Todd J. Vision"
date: "March 20, 2018"
csl: f1000-research.csl
output:
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  md_document:
    variant: markdown_github
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
bibliography: input_references.bib
---

>>>>

---
title: "Data Archiving Attitudes"
author: "Heather A. Piwowar, Todd J. Vision"
date: "March 20, 2018"
output:
  md_document:
    variant: markdown_github
  html_document:
    css: style.css
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
csl: f1000-research.csl
bibliography: input_references.bib
---
